### 2019-03-22 paper/sex_selection_spacing-ver2.tex
Need discussion of distribution results in Conclusion

\subsection{Distribution of Birth Spacing Within Spells and Across Sex Compositions}

@@

The results show three major, interrelated trends over the last 40 years.
First, fertility has declined for all groups, as shown by the parity progression
probabilities, with a larger decline the more educated the woman.
Across all groups, the likelihood of having an additional child in each spell depends 
strongly on how many sons you already have, with women with none or only one son having
the highest probability of a birth.
Second, there has been a general increase in the length of average birth 
intervals for all education groups.
The increase in average birth interval is larger the higher the spell and the higher the 
education group.
Finally, as shown by the increasing sex ratios for women with no or only one son there
has been a substantial increase in the use of sex selection over time.
As for fertility and birth intervals, this increase is larger the higher the spell and
with higher education.

The results also show two very different approaches to son preference with important
impacts on spacing patterns.
At one extreme, rural women without education mostly follow the standard pattern of 
shorter spacing when a woman does not have the desired number of sons.
The strength of this pattern does, however, depend critically on spell number.
For the second spell, although the average interval after a first-born girl is shorter
than the average interval after a first-born boy, the difference is small.
The differences in spacing is larger for the third spell and largest for the fourth.
For the the fourth spell, the divergence in intervals across sex compositions have 
increased over time, with the largest increases in average intervals for women with 
two or three boys.
There has also been an increase in average spacing for women with only girls, and there
is some limited evidence of biased sex ratios, which suggests that this increases in
spacing follow from the use of sex selection.

@@

TK Distribution results

>>>>

\subsection{Distribution of Birth Spacing Within Spells}

@@

Three major, interrelated trends emerge from the data over the four decades.
First, fertility has declined for all groups, as shown by the parity progression
probabilities, with a larger decline the more educated the woman.
Across all groups, the likelihood of having an additional child in each spell depends 
strongly on how many sons you already have, with women with none or only one son having
the highest probability of a birth.
Second, there has been a general increase in the length of average birth 
intervals for all education groups.
The increase in average birth interval is larger the higher the spell and the higher the 
education group.
Finally, as shown by the increasing sex ratios for women with no or only one son there
has been a substantial increase in the use of sex selection over time.
As for fertility and birth intervals, this increase is larger the higher the spell and
with higher education.

The results show two very different approaches to son preference with important
impacts on spacing patterns.
At one extreme, rural women without education mostly follow the standard pattern of 
shorter spacing when a woman does not have the desired number of sons.
The strength of this pattern does, however, depend critically on spell number.
For the second spell, although the average interval after a first-born girl is shorter
than the average interval after a first-born boy, the difference is small.
The differences in spacing is larger for the third spell and largest for the fourth.
For the the fourth spell, the divergence in intervals across sex compositions have 
increased over time, with the largest increases in average intervals for women with 
two or three boys.
There has also been an increase in average spacing for women with only girls, and there
is some limited evidence of biased sex ratios, which suggests that this increases in
spacing follow from the use of sex selection.

@@

Despite the differences in average spacing across sex compositions of prior children,
the picture of how son preference affects spacing is more complicated than excepted.
First, for the second spell the differences in birth intervals for the first 25 percent of 
births are negligible across sex compositions, despite that these birth intervals are
clearly within the durations considered the most likely to generate adverse outcomes.
Furthermore, there is little difference in this spacing patterns across education.
Hence, most of the divergence in spacing patterns across sex compositions arise from
longer spells, which are likely to have less negative impacts on children and the mother.
Second, one of the side-effects of the extensive use of sex selection for women with eight
or more years of education for the third and fourth spell is that only-girls families
not only end up with longer average intervals to the birth of the next, they also are now
much less likely to have a short, i.e. less than 18 months, interpregnancy interval,
which may reduce the sibling competition for resources.
